\documentclass{letter}
\usepackage{fullpage}
\signature{Daniel Asher Resnick}
\address{104 N Yale Avenue \\ Villa Park, IL 60181 \\ USA}
\longindentation=10pt


\begin{document}
\begin{letter}{}
    \opening{Dear ,}
    I would like to petition to have my winter 2012 term excluded from my record.
    I am seeking this so that my failed course attempts would drop below the maximum allowed,
    thus returning my accademic record to good standing and allowing me to resume my studies.

    Over the past several years I have been formally diagnosed with clinical depression.
    Winter 2012 was before I had this diagnosis,
    or knew the full extent of the symptoms I suffer from.
    I had not yet been seeing a psychologist or taking medication.
    In that term I tried to take 6 courses and a lab, unaware of my limitations,
    and consequently experienced my most acute and debilitating depressive episode to that point.
    This prevented me from attending classes and completing assignments,
    ultimately resulting in 4 failed course attempts.

    I have since had 3 years of treatment from psychologists and psychiatrists,
    medication, and a formal diagnosis.
    I have learned many coping techniques and understand my limitations much better.

    In the Winter 2015 term I exceeded the maximum failed course attempt limit
    and was required to withdraw from the math faculty.
    In May 2015 I moved to Chicago and started seeking employment.
    In short order I received two offers for full-time programming positions
    and I accepted the Programmer 1 position at the Mx Group on August 11.

    In my position at Mx I work on several software projects and
    I consistently meet my responsibilities to my team and our clients.
    I have made my teammates and supervisors aware of my condition
    so that we can plan around them.
    I am in ongoing treatment with a psychiatrist and am continuing to explore
    the best medication combination for me.

    To conclude, in the winter 2012 term I was ill-equipped to handle my depression
    and consequently my academics suffered.
    Since then I have made a lot of progress towards managing it
    and I feel I can now demonstrate my true potential.
    I ask for the opportunity to prove this by returning to school.
    My advisor, Ruxandra Moraru,
    has recommended exclusion of the winter 2012 term from my record
    to be the best way of accomplishing that.

    \closing{Thank you for your consideration,}
\end{letter}
\end{document}
