\documentclass{letter}
\usepackage{fullpage}
\signature{Daniel Asher Resnick}
\address{104 N Yale Avenue \\ Villa Park, IL 60181 \\ USA}
\longindentation=10pt


\begin{document}
\begin{letter}{}
    \opening{To the Standings and Promotions Committee:}
    I would like to petition to have my Winter 2012, Fall 2012 and Winter 2015
    terms zero-credited.  I am seeking this so that my failed course attempts
    would drop below the maximum allowed, thus returning my accademic record to
    good standing and allowing me to resume my studies.

    On November 6\textsuperscript{th} 2012,
    I was formally diagnosed with clinical depression.
    Before I had this diagnosis,
    I didn't know the full extent of the symptoms I suffer from,
    nor had I been seeing a psychologist or taking medication.

    In the Winter 2012 term I tried to take 6 courses and a lab,
    unaware of my limitations, and consequently experienced
    my most acute and debilitating depressive episode to that point.
    This prevented me from attending classes and completing assignments,
    ultimately resulting in 4 failed course attempts.

    In the Fall 2012 term I realized I needed to seek professional help
    and to manage my workload better,
    but it was too late to withdraw from courses at no penalty.
    Nonetheles, withdrawing from some of my courses
    and initiating treatment with a psychologist
    was necessary in order to begin to retake control of my life.

    In the Winter 2015 term I exceeded the maximum failed course attempt limit.
    This was a direct consequence of an ongoing depressive episode that had
    started even before term began.
    Eventually I was overwhelmed and had to stop my studies altogether.

    Since then,
    I have had ongoing treatment from psychologists and psychiatrists;
    I have been taking medication and refining the combination I take;
    I have learned many coping techniques;
    and have come to understand my limitations much better.

    In May 2015 I moved to Chicago and began seeing a psychiatrist.
    I started taking a comprehensive combination of medications
    and it has greatly improved my ability to manage my life.
    I soon started seeking employment,
    and in short order I received two offers for full-time programming positions
    and I accepted the Programmer 1 position at the MX Group on August 11.

    In my position at MX I work on several software projects and
    I consistently meet my responsibilities to my team and our clients.
    I have made my teammates and supervisors aware of my condition
    so that we can plan around them.
    I am in ongoing treatment with a psychiatrist and am continuing to explore
    the best medication combination for me.

    To conclude, I was previously ill-equipped to handle my depression
    and my academics suffered as a result.
    I have since made a lot of progress towards managing it
    and I feel I can now demonstrate my true potential.
    I ask for the opportunity to prove this by returning to school.
    My advisor, Ruxandra Moraru, has recommended zero-crediting my
    Winter 2012, Fall 2012 and Winter 2015 terms.

    \closing{Thank you for your consideration,}
\end{letter}
\end{document}
